\noindent The candidate confirms that the work submitted is their own, except where work which has formed part of jointly authored publications has been included. The contribution of the candidate and the other authors to this work has been explicity indicated below. The candidate confirms that appropriate credit has been given within the thesis where reference has been made to the work of others. 

The following chapters contain jointly authored manuscripts where Caroline Jane Tait is the lead author:
\begin{itemize}
  \item The work in Chapter 3 of the thesis has appeared in publicaton as:  
\end{itemize}

\begin{quote}
\textbf{Tait, C.}, Beecham, R., Lovelace, R. and Barber, S. (2023). Contraflow and cycling safety: Evidence from 22 years of data involving 508 one-way streets. \emph{Accident Analysis \& Prevention}, 179, 106895, https://doi.org/10.1016/j.aap.2022.106895.
\end{quote}

\begin{quote}
\textbf{Caroline Jane Tait} was the lead author and responsible for conceptualisation, primary data creation, writing, data analysis, visualisation, review and editing. Drs Roger Beecham, Robin Lovelace and Stuart Barber supervised the research and provided editorial and advisory comments.  
\end{quote}

\begin{itemize}
  \item The work in Chapter 4 of the thesis is formatted and ready for submission pending feedback from all contributing authors as:  
\end{itemize}

\begin{quote}
\textbf{Tait, C.}, Beecham, R., Lovelace, R. and Barber, S. (2023). Build it but will they come? Exploring the impact of introducing contraflow cycling on cycling volumes with crowdsourced data. \emph{Intended submission to: Journal of Transport \& Health}.
\end{quote}

\begin{quote}
\textbf{Caroline Jane Tait} was the lead author and responsible for conceptualisation, writing, data analysis, visualisation, review and editing. Drs Roger Beecham, Robin Lovelace and Stuart Barber supervised the research and provided editorial and advisory comments.  
\end{quote}

This copy has been supplied on the understanding that it is copyright material and that no quotation from the thesis may be published without proper acknowledgement. 

\copyright  2023 The University of Leeds, Caroline Jane Tait


